---
title: "Homework 1"
author: Jenesis Merriman
date: September 24,2022
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Problem 1

First, I will load the "penguins" dataset:

```{r load}
data("penguins", package = "palmerpenguins") #load
```
### Data Overview
The data in this dataset includes information about penguins, measured across `r ncol(penguins)` variables. 

There are `r nrow(penguins)` observations (rows) and `r ncol(penguins)` variables (columns) in the data set. Variables include species, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex, and year.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

### Scatterplot

The following scatterplot displays the relationship between bill length (mm) and flipper length (mm) for penguins in the data set, color coded by species. 

```{r scatter, message = FALSE, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() #plot

ggsave("scatter_plot.pdf") #save
```
Overall, the scatterplot displays a moderately strong, positive relationship between bill length and flipper length among penguins in our data set.

## Problem 2

For this problem, I will first create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r data frame}
p2_df = tibble(
  norm_samp = rnorm(10),
  vec_log = norm_samp > 0,
  vec_char = c("low", "medium", "high", "high", "low", "medium", "medium", "low", "high", "medium"),
  vec_fac = factor(vec_char, levels = c("low", "medium", "high"))
  )

print(p2_df)
```

### Variable Means
Now I will try to take the mean of each variable:

```{r means}
mean(pull(p2_df, norm_samp))
mean(pull(p2_df, vec_log))
mean(pull(p2_df, vec_char))
mean(pull(p2_df, vec_fac))
```

Using this code, I can generate the mean of the numeric vector (norm_samp) and logical vector (vec_log). This code does **not** work for the character vector (vec_char) and factor vector (vec_fac).

### Converting Variables

In some cases, R can explicitly convert variables from one type to another. Here I will apply the *as.numeric()* function to the logical, character, and factor variables:

```{r convert, eval = FALSE}
as.numeric(p2_df$vec_log)
as.numeric(p2_df$vec_char)
as.numeric(p2_df$vec_fac)
```

The *as.numeric()* function successfully converts the logical (vec_log) and factor vectors (vec_fac) into numeric vectors. The character vector (vec_char) does not convert successfully and results in a string of "NA".

This helps explain my results above when taking means for each variable in the {r means} code chunk. It did **not** work for the character vector and factor vector because these variables were not numeric or logical. After coercion, however, the mean of the converted factor vector can be taken and is returned as `r mean(as.numeric(p2_df$vec_fac))`.

