---
title: "Homework 1"
author: Jenesis Merriman
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

First, I will load the penguin dataset:

```{r}
data("penguins", package = "palmerpenguins") #load

print(penguins) #display
```
## Data Overview
The data in this dataset includes information about penguins. 

Variables for each observation include species, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex, and year. There are 344 observations (rows) and 8 variables (columns) in the data set.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Scatterplot
```{r scatter}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```
This scatterplot displays the relationship between bill length (mm) and flipper length (mm) for penguins in the data set, color coded by species. Overall, the scatterplot displays a moderately strong, positive relationship between bill length and flipper length.

# Problem 2

I can take the mean of the sample, too!
The mean is `r mean(sample)`.