---
title: "Homework 1"
author: Jenesis Merriman
date: September 24,2022
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

First, I will load the penguin dataset:

```{r load}
data("penguins", package = "palmerpenguins") #load
```
## Data Overview
The data in this dataset includes information about penguins, measured across `r ncol(penguins)` variables. 

There are `r nrow(penguins)` observations (rows) and `r ncol(penguins)` variables (columns) in the data set. Variables include species, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex, and year.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Scatterplot
```{r scatter, message = FALSE, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() #plot

ggsave("scatter_plot.pdf") #save
```
This scatterplot displays the relationship between bill length (mm) and flipper length (mm) for penguins in the data set, color coded by species. Overall, the scatterplot displays a moderately strong, positive relationship between bill length and flipper length among penguins in our data set.

# Problem 2

For this problem, I will first create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r data frame}
p2_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_lv = norm_samp > 0,
  vec_char = c("low", "medium", "high", "high", "low", "medium", "medium", "low", "high", "medium"),
  vec_fac = factor(vec_char, levels = c("low", "medium", "high"))
  )
```

Now I will try to take the mean of each variable:

```{r means}
mean(pull(p2_df, norm_samp))
mean(pull(p2_df, norm_samp_lv))
mean(pull(p2_df, vec_char))
mean(pull(p2_df, vec_fac))
```

Using this code, I can see the mean of the random sample (norm_samp) and logical vector (norm_samp_lv). These are -0.4 and 0.3, respectively. This code does **not** work for the character vector (vec_char) and factor vector (vec_fac) because these variables are not numeric or logical.






