---
title: "Homework 1"
author: Jenesis Merriman
date: September 24,2022
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

First, I will load the penguin dataset:

```{r load}
data("penguins", package = "palmerpenguins") #load
```
## Data Overview
The data in this dataset includes information about penguins, measured across `r ncol(penguins)` variables. 

There are `r nrow(penguins)` observations (rows) and `r ncol(penguins)` variables (columns) in the data set. Variables include species, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex, and year.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Scatterplot
```{r scatter, message = FALSE, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf")
```
This scatterplot displays the relationship between bill length (mm) and flipper length (mm) for penguins in the data set, color coded by species. Overall, the scatterplot displays a moderately strong, positive relationship between bill length and flipper length.

# Problem 2

I can take the mean of the sample, too!
The mean is `r mean(sample)`.